---
title: "Moderate-Intensity Statin with Ezetimibe Combination Therapy vs High-Intensity Statin Monotherapy in ASCVD Patients"
subtitle: "Randomized, open-label, non-inferiority trial"
author: "Chaeeon Lee"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    df-print: paged
  docx:
    toc: true
    toc-depth: 3
    number-sections: true
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false

library(data.table)
library(magrittr)
library(flextable)
library(ggplot2)

source("analysis.R")

set_flextable_defaults(
  font.size = 10,
  padding = 3
)
```

# Overview

This report is a Quarto starter template. Replace the demo data import in `global.R`, update `varlist`, and rerun this document.

# Baseline Characteristics

```{r}
#| label: tbl-baseline

ft_list[["Table1_Baseline"]]
```

# Survival Analysis

```{r}
#| label: tbl-cox

ft_list[["Table2_Cox"]]
```

```{r}
#| label: fig-km
#| fig-cap: "Kaplan-Meier curve by sex"
#| fig-width: 8
#| fig-height: 6

plot_list[["Figure1_KM"]]
```

# Result Summary

- Replace this section with the main numerical findings after checking the final tables.
- Keep interpretation consistent with the model and endpoint definitions.
- Exported files are saved as `Tables.xlsx` and `Figures.pptx` when `analysis.R` is sourced.

# Statistical Analysis

Baseline characteristics were summarized as median (interquartile range) for continuous variables and number (percentage) for categorical variables. Continuous variables were compared using the Wilcoxon rank-sum test, and categorical variables were compared using the chi-squared test or Fisher's exact test, as appropriate. Time-to-event outcomes were analyzed using Kaplan-Meier curves and compared using the log-rank test. Hazard ratios and 95% confidence intervals were estimated using Cox proportional hazards regression.

All analyses were performed using R 4.5.2 (R Foundation for Statistical Computing, Vienna, Austria).
